Catchability_ecov_sims

### 2023-12-01 Ecov_study/catchability/Catchability_ecov_sims.Rmd

Load packages & source functions used in simulation testing
```{r}
## Packages
library(tidyverse)
library(wham)
library(TAF)
library(varhandle)

@@

## Simulation testing functions
source(here::here("Ecov_study","catchability","simOM.R"))
#source(here::here("Other_Research", "simOM.R"))
source(here::here("Ecov_study","catchability","simTestWHAM.R"))
#source(here::here("Other_Research", "simTestWHAM.R"))
```

@@

#### Amanda run Fhist = H-L simulations
```{r}
# Set number of simulations to run
nsim <- 2 # 2

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% filter(Ecov_effect != 0) %>%
  filter(OMname >100)
# %>% head(n=10)
subsetOM <- subsetOM[8:nrow(subsetOM),] #7?

@@

```{r}
# ID all simulation result files 
 files <- list.files(path = here::here(), pattern = "simWHAM_", recursive = TRUE)

perfMet <- postprocess_simTestWHAM(filenames = files)

@@

If results processed in batches/on multiple computers use combinePerfMet to combine final results
```{r}

@@

### Plot results
```{r}
plotResults(results = perfMet, convergedONLY = TRUE)
```

>>>>

# Load packages & source functions used in simulation testing
```{r}
## Packages
library(tidyverse)
library(wham)
library(TAF)
library(varhandle)

@@

## Simulation testing functions
source(here::here("Ecov_study","catchability","simOM.R"))
source(here::here("Ecov_study","catchability","simTestWHAM.R"))

## Processing functions
source(here::here("Ecov_study", "catchability", "postprocess_simTestWHAM.R"))
source(here::here("Ecov_study", "catchability", "combinePerfMet.R"))
source(here::here("Ecov_study", "catchability", "plotResults.R"))
```

@@

#### Amanda run Fhist = H-L simulations
```{r}
# Set number of simulations to run
nsim <- 2

# Subset of OMs to run
subsetOM <- OMsetup %>% filter(F_hist == "H-L") %>% filter(Ecov_effect != 0) %>% tail(n=3)# %>% filter(OMname >100)
# %>% head(n=10)
# subsetOM <- subsetOM[8:nrow(subsetOM),] #7?

@@

```{r}
# Find all result files
filenames1 <- list.files(path = here::here("Ecov_study/catchability/remote1_Results"), pattern = "simWHAM_", recursive = TRUE, full.names = TRUE)
filenames2 <- list.files(path = here::here("Ecov_study/catchability/remote2_Results"), pattern = "simWHAM_", recursive = TRUE, full.names = TRUE)
filenames3 <- list.files(path = here::here("Ecov_study/catchability/remote3_Results_supplementalRuns"), pattern = "simWHAM_", recursive = TRUE, full.names = TRUE) # simulations to fill gaps so 100 simulations for each OM/EM pair

# Set storage directory
outdir = here::here("Ecov_study/catchability")

# Post-process results
postprocess_simTestWHAM(filenames = c(filenames1, filenames2, filenames3), outdir = outdir)

# Try running in the console if this causes an "Error... cannot open the connection) 
```

@@

If results processed in batches/on multiple computers use combinePerfMet to combine final results
```{r}
# ID all processed performance metric files in "Results" folder
 files <- list.files(path = here::here(), pattern = "perfMet_", recursive = TRUE)

combinePerfMet(filenames = files, outdir = here::here("Ecov_study", "catchability", "Results"))

@@

### Plot results
168 Ecov has 150 simulation
192?
2 qRandEcov only has 50 - fixed
49 qRandEcov only has 50 - fixed
192 qRand, qRandEcov only has 50
```{r}
perfMet <- readRDS(here::here("Ecov_study", "catchability", "perfMet_2023-11-29_13-57-01.735372.RDS"))
  # readRDS(here::here("Ecov_study", "catchability", "perfMet_2023-11-28_09-32-17.294206.RDS"))

library(TAF)
mkdir(here::here("Ecov_study", "catchability", "plots"))

plotResults(results = perfMet, convergedONLY = TRUE, outfile = here::here("Ecov_study", "catchability", "plots"))
```
